RadLib: a radiative property model library for CFD

### 2021-09-14 manuscript/manuscript.tex
Grammar, usage, and proofreading edits for clarity in Sections 2.2, 2.3, 2.4, and 3

    \begin{table}
        \caption{Summary of radiative property models in RadLib and the range of conditions under which they can be
        applied.}
        \label{t:models}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{l l l l}
                \hline
                Model & T range & P range & Refs.   \\
                \hline
                PM      & 300\textendash 2500 K & 1 atm               & \cite{TNF} \\
                WSGG    & 300\textendash 2400 K & 1 atm               & \cite{Bordbar_2020,Bordbar_2014} \\
                RCSLW   & 300\textendash 3000 K & 0.1\textendash 50 atm &  \cite{Solovjov_2017} \\
                \hline
            \end{tabular}
        }
    \end{table}

@@

    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}).
    RadLib implements the WSGG model presented by Bordbar et al. \citep{Bordbar_2014,Bordbar_2020}. This model computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010 database \cite{Rothman_2010}. The $k_j$ and $a_j$ are then correlated to these results using polynomial fits summarized below. The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant radiatively participating species in most combustion environments, using four gray gases and one clear gas. Absorption coefficients are calculated by
%
    \begin{linenomath}
        \begin{equation}
            \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
        \end{equation}
    \end{linenomath}
%
    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$. The weight factors are calculated by
%
    \begin{linenomath}
        \begin{equation}
            a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
        \end{equation}
    \end{linenomath}
%
    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K. The valid temperature range of the model is 300-2400 K; temperatures outside this range use the value at the respective bound. The value of $b_{i,j}$ is calculated by
%
    \begin{linenomath}
        \begin{equation}
            b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
        \end{equation}
    \end{linenomath}
%
    where $C_{j,k,i}$ is a correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are provided by Bordbar et~al. \citep{Bordbar_2014,Bordbar_2020} but updated values are used in RadLib.

    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility. Most WSGG models are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values. This is true of Bordbar et al.'s 2014 model \cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$. That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG model versions.
    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values by interpolating $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of the correlated range, and that is the model implemented here.

@@

    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases, but differ in the way the gray gases are constructed. In traditional WSGG models, the component gases are only conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}. In SLW approaches, however, the gases are gray in a given spectral band by construction. Rather than defining a gray gas $j$ by integrating over a band of sequential wavenumbers $\eta$ (which may have highly variable absorption coefficients), SLW models define a gray gas $j$ by integrating over a set of nonsequential wavenumbers that correspond to a given band of the absorption cross section $C_{\eta}$ with values constant to within the width of the band.

@@

    For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of its component absorption cross sections \cite{Solovjov_2000}. The RCSLW implementation considers \ce{H2O}, \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
%
    \begin{linenomath}
        \begin{equation}
            \label{e:multiC}
            C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
        \end{equation}
    \end{linenomath}
%
    where $x$ denotes mole fraction.
    Assuming that the absorption cross sections of each species are statistically independent, the mixture ALBDF for a given gray gas can be computed using the multiplication method \cite{Solovjov_2000}:
%
    \begin{linenomath}
        \begin{equation}
            \label{e:multiF}
            F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right).
        \end{equation}
    \end{linenomath}
%
    Here, the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.

    The spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}) assumes the sets $\Delta_j$ are independent of spatial position $\mathbf{x}$, but $C_\eta$ depends on the thermodynamic state (denoted by vector $\BS{\phi}$), which does vary spatially.
%That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$. 
    Hence, a spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and $\tilde{C}_j$.
    The RCSLW model uses the notion of rank correlation to handle this spatial variation in the ALBDF.
    Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ with corresponding absorption cross section spectra $C_\eta(\eta,\BS{\phi}_1)$, and $C_\eta(\eta,\BS{\phi}_2)$ and let $\hat{C}_1\equiv C_\eta(\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some wavenumber $\hat{\eta}$. For each spectrum, we define the set of wavenumbers that give cross sections less than $\hat{C}$ as
%
    \begin{linenomath}
        \begin{align}
            H_1&=\{\eta: C_\eta(\eta,\BS{\phi}_1)<\hat{C}_1\}, \\
            H_2&=\{\eta: C_\eta(\eta,\BS{\phi}_2)<\hat{C}_2\}.
        \end{align}
    \end{linenomath}
%
    If $H_1=H_2$ for an arbitrary $\hat{\eta}$, then the spectra $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are said to be rank correlated.
% Solovjov provides some visual representations...

@@

    In the Planck Mean model, which treats a gas mixture as one gray gas, the soot absorption coefficient calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient. Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ with units of \si{m^{-1}}.

@@

    RadLib installation is automated with CMake as follows. Inside the downloaded \texttt{radlib} folder, the user creates and enters a \texttt{build} directory, then enters the commands \texttt{cmake ..}, followed by \texttt{make}, followed by \texttt{make install}. Project options are specified by editing the top-level \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed}; options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and an option to build the documentation. Included \texttt{Readme.md} files provide additional information.

    The code installation folder includes directories \texttt{include} containing header files and a Fortran module file, \texttt{lib} containing library files for each interface, \texttt{cmake} with relocatable CMake files for downstream usage, and \texttt{rcslw\textunderscore data} containing binary data files used by the RCSLW model. These binary files contain the ALBDF functions for a given species at a given pressure (in atm units), as indicated by the file name. The \texttt{include} directory contains the following interface header and module (Fortran) files:
%
    \begin{itemize}
        \item \texttt{rad\textunderscore planck\textunderscore mean.h},
        \item \texttt{rad\textunderscore wsgg.h},
        \item \texttt{rad\textunderscore rcslw.h},
        \item \texttt{rad\textunderscore module.mod}.
    \end{itemize}
%
    The C++ and Fortran libraries in the \texttt{lib} folder are
    \begin{itemize}
        \item \texttt{libradlib.a},
        \item \texttt{libradlib\textunderscore fortran.a}.
    \end{itemize}
%
    This folder also contains the Python module. If the Python interface is built, the location of the installed Python package needs to be added to the \texttt{PYTHONPATH} environment variable. A command to do this is provided at the end of the installation.

    To use RadLib in C++, a user code includes the header file for the desired radiation model, e.g., \texttt{\#include "rad\textunderscore rcslw.h"}. For Fortran, a \texttt{use rad\textunderscore module} statement provides access to the required interface functions. The Python interface functions are loaded from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}. Such usage is demonstrated in the code listing for the examples discussed below. Compilation of C++ and Fortran programs requires specification of the header/module and library directory locations and linking against the installed libraries (\texttt{libradlib.a} for C++ and both \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a} for Fortran).

    Figure \ref{fig:flowchart} illustrates the basic structure of using RadLib in a generic one-dimensional RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an appropriate RTE solver. A user first creates a radiation object, and then makes calls to one of two primary functions: \texttt{get\textunderscore k\textunderscore a()}, or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
    These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The WSGG model does not account for \ce{CO} or \ce{CH4}, and only the PM model includes \ce{CH4}. A uniform interface is facilitated by giving default values of 0.0 for the \ce{CO} and \ce{CH4} mole fraction parameters so that these do not need to be specified for models that do not make use of them. The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of absorption coefficients and a vector of weight factors, with elements corresponding to each clear and gray gas considered in the model (with the clear gas coming first). The PM model only considers one gas and the vectors are of unity size. The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} computes the absorption coefficient and weight factor (as scalar values) for a single gas (or \emph{band}), whose index (starting at zero for all interfaces) is provided as an additional argument. This option to compute the properties for a single gas/band can be important for efficient implementation in some solvers, e.g., in the Fire Dynamics Simulation (FDS), discussed below \cite{FDS}. The absorption coefficients and weights are set through the function argument list for the C++ and Fortran interfaces, and as return values for the Python interface. Additional details are included in the program documentation and code listing.
%
    \begin{figure}
        \begin{center}
            \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
        \end{center}
        \caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
        \label{fig:flowchart}
    \end{figure}
%

    The RadLib source code is build around a base class called \texttt{rad} from which the individual property models, e.g., \texttt{rad\textunderscore rcslw}, inherit.
    To extend RadLib to include new radiative property models, a user would create a new derived class for the model that inherits from the \texttt{rad} base class. The interface functions \texttt{get\textunderscore k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} would be reimplemented in the new model. Additional functions and capabilities could be added as desired. The Fortran and Python interface codes consist of wrapper functions to the underlying C++. These can be easily extended by paralleling the existing interface functions.

>>>>

    \begin{table}
        \caption{Summary of radiative property models in RadLib and the range of conditions under which they can be
        applied.}
        \label{t:models}
        \centering
        \resizebox{\textwidth}{!}{
            \begin{tabular}{l l l l l}
                \hline
                Model & T range & P range & Gas species & Refs.   \\
                \hline
                PM    & 300\textendash 2500 K & 1 atm & \ce{CO2}, \ce{H2O}, \ce{CO}, \ce{CH4} & \cite{TNF} \\
                WSGG  & 300\textendash 2400 K & 1 atm & \ce{CO2}, \ce{H2O} & \cite{Bordbar_2014,Bordbar_2020} \\
                RCSLW & 300\textendash 3000 K & 0.1\textendash 50 atm & \ce{CO2}, \ce{H2O}, \ce{CO} & \cite{Solovjov_2017} \\
                \hline
            \end{tabular}
        }
    \end{table}

@@

    Weighted sum of gray gases (WSGG) models generate radiation absorption coefficients for use with the spectrally
    integrated RTE (Eq.~\ref{e:RTE_wsgg}).
    RadLib implements the WSGG model presented by Bordbar et al.~\citep{Bordbar_2014,Bordbar_2020}. This model
    computes emissivity for varying gas temperature, mixture composition, and path length using the HITEMP 2010
    database~\cite{Rothman_2010}. The $k_j$ and $a_j$ values are correlated to these results using polynomial fits as
    summarized below. The model considers mixtures of gaseous \ce{CO2} and \ce{H2O}, the two most significant
    radiatively participating species in most combustion environments, using four gray gases and one clear gas.
    Absorption coefficients are calculated by
%
    \begin{linenomath}
        \begin{equation}
            \kappa_j=\sum_{k=0}^{4}d_{j,k}M_r^k,
        \end{equation}
    \end{linenomath}
%
    where $\kappa_j$ is the absorption coefficient for gray gas $j$, $d_{j,k}$ is a correlated model coefficient, and
    $M_r$ is the molar ratio $x_{\mathrm{H_2O}}/x_{\mathrm{CO_2}}$. The weight factors are calculated by
%
    \begin{linenomath}
        \begin{equation}
            a_j=\sum_{k=0}^{4}b_{j,k}T_r^k,
        \end{equation}
    \end{linenomath}
%
    where $a_j$ is the weighting factor for gas $j$, $b_{i,j}$ is computed as shown below,  and $T_r$ is a scaled
    temperature equal to $T/T_{ref}$ with $T_{ref}$=1200 K. The value of $b_{i,j}$ is calculated by
%
    \begin{linenomath}
        \begin{equation}
            b_{j,k}=\sum_{i=0}^{4}C_{j,k,i}M_r^i,
        \end{equation}
    \end{linenomath}
%
    where $C_{j,k,i}$ is a correlated model coefficient. The model coefficients $d_{j,k}$ and $C_{j,k,i}$ are
    provided by Bordbar~et~al.~\citep{Bordbar_2014,Bordbar_2020}; RadLib uses updated values
    in~\cite{Bordbar_2020}. The model is valid for temperatures between 300 K and 2400 K; temperatures outside this range use the value at the respective bound.

    This particular WSGG model was chosen for RadLib for its performance, accuracy, and flexibility. Most WSGG models
    are limited to specific values of the molar \ce{H2O}--\ce{CO2} ratio, or to a limited range of values. This is
    true of Bordbar et al.'s 2014 model~\cite{Bordbar_2014}, which used correlations valid for $0.01\le M_r\le4$.
    That paper summarizes a number of WSGG models and gives the applicable molar ratio range for several recent WSGG
    model versions.
    Bordbar et al.~\citep{Bordbar_2020} extended the molar ratio range to arbitrary values of $M_r$ by interpolating
    $\kappa_j$ and $a_j$ between the pure component values and the corresponding limit on $M_r$ for values outside of
    the correlated range. RadLib implements this extended version of the model.

@@

    SLW and WSGG models are similar in that they approximate real gas mixtures with a set of radiatively gray gases,
    but differ in the way that the gray gases are constructed. In traditional WSGG models, the component gases are only
    conceptually gray, and the absorption coefficients and weights are determined empirically \citep{Badger_2019}. In SLW approaches, however, the gases are gray in a given spectral band by construction. Rather than defining a gray gas $j$ by integrating over a band of sequential wavenumbers $\eta$ (which may have highly variable absorption coefficients), SLW models define a gray gas $j$ by integrating over a set of nonsequential wavenumbers that correspond to a given band of the absorption cross section $C_{\eta}$ with values constant to within the width of the band.

@@

    For multicomponent gas mixtures, the mixture absorption cross section $C_{\eta}$ is defined as a weighted sum of
    its component absorption cross sections \cite{Solovjov_2000}. RadLib's RCSLW implementation considers \ce{H2O},
    \ce{CO2}, and \ce{CO}, for which the mixture absorption cross section for a given gray gas is given by
%
    \begin{linenomath}
        \begin{equation}
            \label{e:multiC}
            C_{\eta} = x_{\ce{CO2}}C_{\ce{CO2},\eta} + x_{\ce{H2O}}C_{\ce{H2O},\eta} + x_{\ce{CO}}C_{\ce{CO},\eta},
        \end{equation}
    \end{linenomath}
%
    where $x$ denotes mole fraction.
    Assuming that the absorption cross sections of each species are statistically independent, the mixture ALBDF for a given gray gas can be computed using the multiplication method \cite{Solovjov_2000}:
%
    \begin{linenomath}
        \begin{equation}
            \label{e:multiF}
            F_{\eta}(C_{\eta}) = F_{\ce{CO2},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO2}}} \right) F_{\ce{H2O},\eta} \left( \frac{C_{\eta}}{x_{\ce{H2O}}} \right) F_{\ce{CO},\eta} \left( \frac{C_{\eta}}{x_{\ce{CO}}} \right).
        \end{equation}
    \end{linenomath}
%
    Note that the $\BS{\phi}$ and $T$ arguments of $F$ are omitted from Eq.~\ref{e:multiF} for clarity.

    The spectrally integrated RTE (Eq.~\ref{e:RTE_wsgg}) assumes the sets $\Delta_j$ are independent of spatial position $\mathbf{x}$, but $C_\eta$ depends on the thermodynamic state (denoted by vector $\BS{\phi}$), which does vary spatially.
%That is, $C_\eta=C_\eta(\eta,\BS{\phi}(\mathbf{x}))$. 
    Hence, a spatially-fixed $\Delta_j$ with spatially varying $\BS{\phi}$ implies a spatial variation in $C_j$ and
    $\tilde{C}_j$.
    The RCSLW model uses the notion of rank correlation to handle this spatial variation in the ALBDF.
    Consider two positions with thermodynamic states $\BS{\phi}_1$ and $\BS{\phi}_2$ with corresponding absorption
    cross section spectra $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$, and let $\hat{C}_1\equiv C_\eta
    (\hat{\eta},\BS{\phi}_1)$ and $\hat{C}_2\equiv C_\eta(\hat{\eta},\BS{\phi}_2)$ denote the cross sections at some
    wavenumber $\hat{\eta}$. For each spectrum, we define the set of wavenumbers that give cross sections less than
    $\hat{C}$ as
%
    \begin{linenomath}
        \begin{align}
            H_1&=\{\eta: C_\eta(\eta,\BS{\phi}_1)<\hat{C}_1\}, \\
            H_2&=\{\eta: C_\eta(\eta,\BS{\phi}_2)<\hat{C}_2\}.
        \end{align}
    \end{linenomath}
%
    If $H_1=H_2$ for an arbitrary $\hat{\eta}$, then the spectra $C_\eta(\eta,\BS{\phi}_1)$ and $C_\eta(\eta,\BS{\phi}_2)$ are said to be rank correlated.
% Solovjov provides some visual representations...

@@

    In the PM model, which treats a gas mixture as a single gray gas, the soot absorption coefficient
    calculated from Eq.~\ref{e:soot2} is simply added to the gas absorption coefficient. Using the given values of $C_0$ and $C_2$ above, the expression for the soot absorption coefficient simplifies to  $\kappa_s=1817f_vT$ with units of \si{m^{-1}}.

@@

    RadLib installation is automated with CMake. Inside the downloaded \texttt{radlib} folder, the user must create a
    \texttt{build} directory and navigate into it. From there, the user executes the following commands in order:
    \begin{enumerate}
        \item \texttt{cmake ..}
        \item \texttt{make}
        \item \texttt{make install}
    \end{enumerate}
    Project options can specified by editing the top-level
    \texttt{CMakeLists.txt} file where the options are clearly marked. These can also be specified at the command
    line. Options include specifying the system installation location, which defaults to \texttt{radlib/installed};
    options to build the Python and Fortran interfaces; options to build examples for C++, Python, and Fortran; and
    an option to build the documentation. Refer to the included \texttt{README} files for additional information.

    Following successful installation, the installation folder will contain four directories:
    \texttt{cmake} contains relocatable CMake files for downstream developer use;
    \texttt{include} contains the C++ header files and a Fortran module file;
    \texttt{lib} contains library files for each interface, including the python module files;
    and \texttt{rcslw\textunderscore data} contains the binary data files used by the RCSLW model, each of which
    contains the tabulated ALBDF functions for a given species at a given pressure (in units of atm) as indicated by
    the file name. If the Python interface is built, the location of the installed Python package must be added
    to the \texttt{PYTHONPATH} environment variable. A command instructing the user how to do this is provided at the end of
    the installation. The following outline further illustrates the organization of the installation folder and file
    locations therein:
%
    \begin{itemize}
        \item \texttt{cmake}
        \begin{itemize}
            \item \texttt{radlib}
            \begin{itemize}
                \item \texttt{radlib.cmake}
            \end{itemize}
            \item \texttt{radlib\textunderscore fortran}
            \begin{itemize}
                \item \texttt{radlib\textunderscore fortran.cmake}
            \end{itemize}
        \end{itemize}
        \item \texttt{include}
        \begin{itemize}
            \item \texttt{rad\textunderscore planck\textunderscore mean.h}
            \item \texttt{rad\textunderscore wsgg.h}
            \item \texttt{rad\textunderscore rcslw.h}
            \item \texttt{rad\textunderscore module.mod}
        \end{itemize}
        \item \texttt{lib}
        \begin{itemize}
            \item \texttt{libradlib.a}
            \item \texttt{libradlib\textunderscore fortran.a}
            \item \texttt{python[version]}
            \begin{itemize}
                \item \texttt{site-packages}
                \begin{itemize}
                    \item \texttt{pyrad.cpython-[system architecture].so}
                \end{itemize}
            \end{itemize}
        \end{itemize}
        \item \texttt{rcslw\textunderscore data}
    \end{itemize}
%
    To use RadLib in C++ code, the user must include the header file for the desired radiation model, e.g.,
    \texttt{\#include "rad\textunderscore rcslw.h"}, in their code. Compilation requires specification of the header
    and library directory locations and linking against the installed library (\texttt{libradlib.a}). In Fortran,
    a \texttt{use rad\textunderscore module} statement provides access to the required interface functions. To
    compile, the module and library locations must be specified and the code linked against both
    \texttt{libradlib.a} and \texttt{libradlib\textunderscore fortran.a}. The Python interface functions are loaded
    from the \texttt{pyrad} module, as in \texttt{from pyrad import pyrad\textunderscore rcslw}. The examples
    included with the RadLib package and discussed in Section~\ref{s:Examples} demonstrate these usages.

    Figure \ref{fig:flowchart} illustrates the basic structure of RadLib in the context of a generic, one-dimensional
    RTE solution. The RadLib library generates absorption coefficients and their weighting factors for use within an
    appropriate RTE solver. To use it, a user first creates a \texttt{radiation} object and then makes calls to
    one of two primary functions: \texttt{get\textunderscore k\textunderscore a()} or \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()}.
    These two functions take the arguments for temperature (K), pressure (Pa), soot volume fraction, and mole
    fractions of \ce{H2O}, \ce{CO2}, \ce{CO}, and \ce{CH4}. The \ce{CO} and \ce{CH4} mole fraction
    parameters have default values of zero and do not need to be specified for models that do not make use of them
    (see Table~\ref{t:models}). The \texttt{get\textunderscore k\textunderscore a()} function computes a vector of
    absorption coefficients and a vector of weight factors in which each element corresponds to one of the gray gases
    considered in the model (with the clear gas in the first position). The PM model only considers one gray gas and
    thus returns vectors containing one element each.
    The \texttt{get\textunderscore k\textunderscore a\textunderscore oneband()} function computes the
    absorption coefficient and weight factor as scalar values for a single gray gas whose index
    (starting at zero for all interfaces) is provided as an additional argument. This option to compute the
    properties for a single gray gas can be important for efficient implementation in some solvers, including Fire
    Dynamics Simulator (FDS), discussed below~\cite{FDS}.
    In C++ and Fortran, the absorption coefficients and weights are set through the function argument list; in
    Python, they appear as return values from the functions. For additional details, refer to the software
    documentation.
%
    \begin{figure}
        \begin{center}
            \includegraphics[width=\textwidth]{fig_radlib_structure.pdf}
        \end{center}
        \caption{Example workflow diagram. Highlighted areas are part of the RadLib library; other areas represent example infrastructure for using the package.}
        \label{fig:flowchart}
    \end{figure}
%

    To extend RadLib to include new radiative property models, a user would create a new derived class
    that inherits from the \texttt{rad} base class. The interface functions \texttt{get\textunderscore
    k\textunderscore a} and \texttt{get\textunderscore k\textunderscore a\textunderscore oneband} must be
    reimplemented for the new model. Additional functions and capabilities could be added as desired. The Fortran and
    Python interface codes consist of wrapper functions to the underlying C++ that can be easily extended in parallel
    to the existing interface functions.
